Cross-validation of regression models: mixed model examples (edited v3)

### 2024-08-18 scratch/JSS-submission/Fox-Monette-cv-package.Rmd
added 'compared' with a model fit to $n$ cases.

Because the $n$ models are each fit to $n - 1$ cases, LOO CV produces a nearly unbiased estimate of the prediction error with a model fit to $n$ cases. The $n$ regression models are highly statistically dependent, however, based as they are on nearly the same data, and so the resulting estimate of prediction error has larger variance than if the predictions from the models fit to the $n$ data sets were independent.

>>>>

Because the $n$ models are each fit to $n - 1$ cases, LOO CV produces a nearly unbiased estimate of the prediction error compared with a model fit to $n$ cases. The $n$ regression models are highly statistically dependent, however, based as they are on nearly the same data, and so the resulting estimate of prediction error has larger variance than if the predictions from the models fit to the $n$ data sets were independent.
